A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-03-31 draft/paper2.tex
Paper split

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH

@@

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Kevin Bundy,$^{3,1}$
        Jenny Greene,$^{4}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Rachel Mandelbaum,$^{6}$
        Michael Strauss,$^{4}$
        and HSC collaboration$^{7}$   
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{6}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{7}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    For the first time, we conclusively show that at fixed stellar mass, massive central 
    galaxies display mass density profiles that are not self similar and which 
    present subtle but systematic differences that correlate with \mhalo{}. 
    On average, massive central galaxies in more massive halos have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
    envelopes. 
    These differences translate into a clear environmental dependence of the mass-size 
    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
    at fixed \mtot{}. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    Furthermore, because galaxies in larger halos have more extended envelopes, 
    the amount of light that is missed will be halo mass dependent. 
    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
    in the amplitude of stellar profiles at 100 kpc. 
    We argue that ``cD'' galaxies represent the tail end of a distribution and 
    are not a distinct class of massive galaxies. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the depth and imaging quality of SDSS and the HSC wide 
            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
            This added depth is critical in order map the outskirts of ETGs out to 
            large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter halos 
    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
    questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

\subsection{The Hyper Suprime-Cam Survey}
    \label{ssec:hsc}

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover ${\sim} 1400$ deg$^2$ 
    in 5 broad bands ($grizY$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec), and the wide area, the HSC survey represents a tremendous data set to 
    perform a large statistical study of the surface brightness profiles of ETGs out to 
    large radii.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We will therefore use the $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{HSC Data Processing}
    \label{sec:pipeline}

    The full details of the HSC data processing can be found in \citet{BoschInPrep}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

    The pixel scale of the combined images is $0.168^{\arcsec}$. 
    Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the coadd level. 
    First, \texttt{hscPipe} performs object detection on coadd images in each band 
    independently and records the flux peak and the above-threshold region 
    (referred as a ``footprint'') for each source. 
    Next, ``footprints'' and peaks from different bands are merged together before     
    performing deblending and measurements. 
    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is 
    the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the coadd image in each band. 
    This forced photometry approach is optimized to yield accurate galaxy colors.

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{BoschInPrep}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the the total flux of massive ETGs (this is discussed further in 
    \citealt{BoschInPrep}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{Initial Massive Galaxy Sample}
    \label{ssec:initial}

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citep{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
    the response curves of SDSS-$i$ and HSC-$i$ filters.}
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample.}.This sample corresponds to 1760845 galaxies and will be referred 
    as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    Here we limit our study to the very high-mass end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} catalog (see Section \ref{ssec:redmapper}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
    different catalogs are homogenized into a single flag that indicates secure 
    redshifts.}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    For objects without a spectroscopic redshift, we match them with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.3 \leq z \leq 0.5$. The accuracy of the red-sequence photo-$z$ is sufficient 
    (median $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with a 
    spec-$z$) for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (will be referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. 
    By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z{\sim} 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.

%% ------------------------------------------------------------------------------------ %%  
\subsection{The \redm{}{} cluster catalog}
    \label{ssec:redmapper}

    Our study focuses on galaxies located at the center of their dark matter halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    The \redm{} catalog therefore helps us group massive central galaxies into 
    samples with different average \mhalo{}. 
    We will use the central galaxies of \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
    live in massive halos.

    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
    To ensure a clean separation in \mhalo{}, here we only focus on the central 
    galaxies of clusters with $\lambda > 30$. 
    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
    We have checked that none of the results in this work depend on the choice of this 
    $\lambda$ limit. 
    For massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
          (red lines).
          }
      \label{fig:smf1}
  \end{figure*}

%% ------------------------------------------------------------------------------------ %% 
\subsection{Massive Central Galaxies in Low and High Mass Halos}
    \label{ssec:mass_central}

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
    live in a fairly broad range of halos masses.
    With the help of the \redm{} catalog, we can broadly separate our sample into two
    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.

    % We match this sample with the central galaxies of \redm{}~catalogs using a 
    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
    galaxies at $0.3 \leq z \leq 0.5$.
    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
    ${\sim} 41$, corresponding to halo mass of 
    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    Out next goal is to construct a sample of central galaxies living in halos with 
    \logmh{}$<14.0$. 
    We first identify and remove all galaxies within a cylindrical region around all 
    \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the uncertainty of the photometric redshift error. 
    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
    \citet{Simet2016} and we use the mass-concentration relation from 
    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
    cluster members.
    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$\leq 14.0$. 
    We will refer to this sample of \textbf{central galaxies in less massive halos}
    as the \nbcg{} sample.

    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
    wide range of \mstar{} values. 
    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
    sample to \logms{}$ > 11.5$. 
    At this very high mass end, and given that we have rejected satellites in \redm{} 
    clusters, any further satellite contamination can be safely neglected 
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
    % TODO: The actual number waits to be updated}

%% ------------------------------------------------------------------------------------ %% 
\subsection{Summary of Sample Construction}
    \label{ssec:sample}

    Using ${\sim} 100$ deg$^2$ of HSC data, we select a large sample of massive central 
    galaxies with reliable redshift information, and broadly separate them two 
    categories based on $M_{\mathrm{halo}}$.

    The following is a summary of our sample construction.

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item \rbcg{} sample: we select a sample of 164 galaxies at 
            $0.3 \leq z \leq 0.5$ that are the central galaxies 
            in $\lambda > 30$ \redm{} clusters. 
            They represent the central galaxies in very massive halos 
            (\logmh{}$\geq 14.2$). 
        \item \nbcg{} sample: after excluding all cluster members from the 
            \texttt{hscZ} sample, we have 14661 bright galaxies at 
            $0.3 \leq z \leq 0.5$. 
            After applying an additional \mstar{} cut (see Section 
            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
            halos with \logmh{}$<14.0$.  
    \end{itemize}

    We now proceed to measure the luminosities and stellar mass profiles for 
    all galaxies in the \rbcg{} and \nbcg{} samples.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Measurements of 1-D Surface Brightness Profiles}
    \label{sec:ellipse}

    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
    as the de~Vaucouleurs model or a single \ser component model. 
    These models will fail to simultaneously capture the profile in both the inner and 
    the outer region and these models also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
    the number of components, initial guesses of parameters, and the internal 
    degeneracies among different parameters. 
    Background subtraction uncertainty can affect the 2-D model fitting dramatically, 
    especially for massive ETGs in our sample. 
    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and measure their one-dimensional profiles of stellar mass surface 
    density (\mden{}). 
    This 1-D method we adopt is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are not sensitive 
    to either the PSF ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).

    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
    radius, along with a bad pixel mask, and the PSF model. 
    These cut-outs include all of the light of the galaxy and are large enough to 
    also evaluate the background level. 
    We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and Y band images (although these in principle may be better tracers of \mden{}).

>>>>

% Version 0; preprint format; Outline of paper II by Song Huang

@@

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Masayuki Tanaka,$^{6}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    For the first time, we conclusively show that at fixed stellar mass, massive central 
    galaxies display mass density profiles that are not self similar and which 
    present subtle but systematic differences that correlate with \mhalo{}. 
    On average, massive central galaxies in more massive halos have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
    envelopes. 
    These differences translate into a clear environmental dependence of the mass-size 
    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
    at fixed \mtot{}. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    Furthermore, because galaxies in larger halos have more extended envelopes, 
    the amount of light that is missed will be halo mass dependent. 
    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
    in the amplitude of stellar profiles at 100 kpc. 
    We argue that ``cD'' galaxies represent the tail end of a distribution and 
    are not a distinct class of massive galaxies. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation. 
    \song{This is the abstract of old draft, need some works}

@@

@@

    \song{This is the old version, need works}
    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter halos 
    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
    questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

@@

@@

    \song{Need a much shorter version of this}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Results}
    \label{sec:results}

    %\footnote{There are different observational definitions of ``environment''. 
    %In this paper, we use the term ``environment'' and halo mass interchangeably}.

    %Previous work has shown that the half-light radii of massive ETGs is tightly 
    %correlated with \mstar{} (e.g. \citealt{Shen2003, Guo2009}). 
    %Models based on the ``two-phase'' formation scenario naturally predict that this 
    %mass--size relation should exhibit an environmental dependence: the effective radii 
    %of massive ETGs in more massive halos should be larger than those in less massive
    %halos at fixed \mstar{} (e.g. \citealt{Shankar2013, Shankar2014}).

    %However, while hints of an environmental dependence in the mass-size relation have 
    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    %also see \citealt{Rettura2010}), there is no solid evidence for this effect at 
    %low-$z$ (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}). 
    %The absence of an environmental dependence in the mass-size relation is an 
    %outstanding challenge to the two-phase formation scenario of ETGs.

    \song{These paragraphs are from Jenny's txt file, need organization.}
    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

    \textbf{Completeness that depends on halo mass:}

    The \rbcg{} sample is less affected by completeness because we can utilize 
    photo-$z$s from \redm{}. 
    However, the completeness of the \nbcg{} sample is still limited by the 
    availability of spec-$z$s from BOSS.

    When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    Please see the next section and Appendix~\ref{app:match} for more details.

%% ------------------------------------------------------------------------------------ %% 
\subsection{Environmental Dependence of the Profiles of Massive Galaxies}
    \label{ssec:sbp_mtot}
